DATA 621 - Business Analytics and Data Mining

### 2020-11-25 Final_project/Draft_EDA_start.Rmd
EDA cleanup

```{r summary_us}
summarygb <- gb_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summarygb)

@@

```{r}
#potential train/test split
ca_set_model <- ca_set %>%
  select(-title, -tags, -channel_title, -trending_date, -publish_time, -video_id, -thumbnail_link, -description, -country)

@@

>>>>

```{r summary_gb}
summarygb <- gb_set%>% select(views, category_id,likes, dislikes, comment_count, comments_disabled, ratings_disabled, view_target, view_global_target, tag_count)
describe(summarygb)

@@

```{r ca_train_split}
#potential train/test split
ca_set_model <- ca_set %>%
  select(-title, -tags, -channel_title, -trending_date, -publish_time, -video_id, -thumbnail_link, -description, -country)

@@

```{r libraries}
```
```{r load_data}
```
```{r ca_data_prep}
```
```{r de_data_prep}
```
```{r fr_data_prep}
```
```{r gb_data_prep}
```
```{r us_data_prep}
```
```{r merge_datasets}
```
```{r global_target}
```
```{r summary_ca}
```
```{r summary_de}
```
```{r summary_gb}
```
```{r summary_fr}
```
```{r summary_us}
```
```{r summary_global}
```
```{r ca_train_split}
```
